%引用(著者アルファベット順にする)
\begin{thebibliography}{3}

\bibitem{IDC_DT_Survey2024}
IDC Japan.
Digital Twin / IoT / AI 技術調査レポート（概要）.
IDC Japan, 2024.

\bibitem{GlobalGrowthInsights_DT}
Global Growth Insights.
Digital Twin Technology Market Trends 2024-2033.
Global Growth Insights, 2024.

\bibitem{ORB_SLAM}
Raul Mur-Artal, J. M. M. Montiel, and Juan D. Tard\'os.
ORB-SLAM: A Versatile and Accurate Monocular SLAM System.
IEEE Transactions on Robotics,
vol. 31, no. 5, pp. 1147--1163, 2015.

\bibitem{ORB_SLAM2}
Raul Mur-Artal and Juan D. Tard\'os.
ORB-SLAM2: An Open-Source SLAM System for Monocular, Stereo, and RGB-D Cameras.
IEEE Transactions on Robotics,
vol. 33, no. 5, pp. 1255--1262, 2017.

\bibitem{CNN_SLAM}
Keisuke Tateno, Federico Tombari, and Nassir Navab.
CNN-SLAM: Real-Time Dense Monocular SLAM with Learned Depth Prediction.
Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR),
pp. 6243--6252, 2017.

\bibitem{Cadena2016}
Cesar Cadena, Luca Carlone, Henry Carrillo, Yasir Latif, Davide Scaramuzza,
Jos\'e Neira, Ian Reid, and John J. Leonard.
Past, Present, and Future of Simultaneous Localization and Mapping:
Toward the Robust-Perception Age.
International Journal of Robotics Research,
vol. 35, no. 14, pp. 1309--1332, 2016.

\bibitem{ImageLocalizationSfM}
Torsten Sattler, Bastian Leibe, and Leif Kobbelt.
Fast Image-Based Localization using Direct 2D-to-3D Matching.
IEEE International Conference on Computer Vision (ICCV),
pp. 667--674, 2011.

\bibitem{ImageRetrievalLocalization}
Herv\'e J\'egou, Matthijs Douze, and Cordelia Schmid.
Aggregating Local Descriptors into a Compact Image Representation.
IEEE Conference on Computer Vision and Pattern Recognition (CVPR),
pp. 3304--3311, 2010.

\bibitem{IndoorSurvey}
Yuan Liu, Wei Dong, Yifan Liu, and Xiaohua Tian.
Image-Based Indoor Localization: A Survey.
IEEE Communications Surveys \& Tutorials,
vol. 22, no. 4, pp. 2923--2955, 2020.

\bibitem{IndoorLiDARNav}
J. Zhang and S. Singh.
LOAM: Lidar Odometry and Mapping in Real-time.
Robotics: Science and Systems (RSS),
pp. 1--9, 2014.

\bibitem{2DMapLocalization}
Paul Biber and Wolfgang Straßer.
The Normal Distributions Transform: A New Approach to Laser Scan Matching.
IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS),
pp. 2743--2748, 2003.

\bibitem{SimplifiedModelLocalization}
Stephan Kohlbrecher, Johannes Meyer, Thomas Graber, et al.
Hector SLAM: Real-Time SLAM with a Single Laser Scanner.
IEEE International Conference on Robotics and Automation (ICRA),
pp. 3987--3994, 2011.

\bibitem{Schindler2007}
Andreas Schindler, Jan-Michael Frahm, and Marc Pollefeys.
City-Scale Location Recognition.
IEEE Conference on Computer Vision and Pattern Recognition (CVPR),
pp. 1--8, 2007.

\bibitem{Sattler2011}
Torsten Sattler, Bastian Leibe, and Leif Kobbelt.
Fast Image-Based Localization using Direct 2D-to-3D Matching.
IEEE International Conference on Computer Vision (ICCV),
pp. 667--674, 2011.

\bibitem{Shewchuk1996Triangle}
Jonathan R. Shewchuk,
Triangle: Engineering a 2D Quality Mesh Generator and Delaunay Triangulator,
in \textit{Applied Computational Geometry: Towards Geometric Engineering},
First ACM Workshop on Applied Computational Geometry,
Lecture Notes in Computer Science, Vol. 1148, pp. 203--222, 1996.

\bibitem{Sugaya2024}
松下侑聖, 菅谷保之, 直交射影に基づく点特徴と線特徴を用いたハイブリッドなカメラ姿勢推定,
第27回画像の認識・理解シンポジウム, 2024年8月.

\bibitem{Lowe2004}
D. G. Lowe,
Distinctive Image Features from Scale-Invariant Keypoints,
International Journal of Computer Vision,
Vol. 60, No. 2, pp. 91--110, 2004.

\bibitem{Alcantarilla2013}
P. F. Alcantarilla,J. Nuevo,A. Bartoli,
Fast Explicit Diffusion for Accelerated Features in Nonlinear Scale Spaces,
British Machine Vision Conference (BMVC), 2013.

\bibitem{DeTone2018SuperPoint}
D.DeTone, T.Malisiewicz, and A.Rabinovich,
SuperPoint: Self-Supervised Interest Point Detection and Description,
arXiv preprint arXiv:1712.07629, 2017.

\bibitem{Sarlin2020SuperGlue}
P.E.Sarlin, D.DeTone, T.Malisiewicz, and A.Rabinovich,
SuperGlue: Learning Feature Matching with Graph Neural Networks,
IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)*, 2020.

\bibitem{matsushita2024}
松下侑聖, 
直交射影に基づく PnPL 問題に対する大域最適解の計算,
pp. 4--11, 2024.

\bibitem{AppleARKitTracking}
Apple Inc.,
Managing Session Life Cycle and Tracking Quality,
Apple Developer Documentation,
\url{https://developer.apple.com/documentation/arkit/managing_session_lifecycle_and_tracking_quality},
（参照日：2026年1月）.

\bibitem{AppleARKitWorldTracking}
Apple Inc.,
Understanding World Tracking,
Apple Developer Documentation,
\url{https://developer.apple.com/documentation/arkit/world_tracking/understanding_world_tracking},
（参照日：2026年1月）.

\bibitem{magsac}
D. Barath, J. Matas, and J. Noskova, 
MAGSAC: marginalizing sample consensus,
IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), 
2019, pp. 10197--10205.

%  \bibitem{bib:sample}加藤博一, ``拡張現実感システム構築ツールARToolKitの開発'',
% 電子情報通信学会研究技術報告, PRMU2001-232, Vol. 101, No. 652, pp. 79--86, 2002.
% 
%  \bibitem{IMA}今泉一崇, ``円形マーカーを用いた複合現実感システムの構築'',
% 豊橋技術科学大学卒業論文, 2008年度.
% 
%  \bibitem{KOBA}小林大起, ``複数の円形マーカーを用いた複合現実感システム
% の構築'', 学士学位論文, 2009年度.
% 
%  \bibitem{IMAKOBA}今泉一崇, 小林大起, 菅谷保之, ``複数の円形マーカーを用いた複合現実感システムの構築'', 第16回画像センシングシンポジウム(SSII10)講演論文集,
% 	 pp. IS2--19, 2010.

\end{thebibliography}
